Title Goes Here

### 2024-05-03 analysis/paper/paper.qmd
add SAA poster and update readme
update figure sizes for URS poster

ggsave(here("analysis",
            "figures", 
            "fig-panel-per-year.png"),
       bg ="white",
       h = 11, # experiment with h and w to get the right size and proportion 
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp

@@

ggsave(here("analysis",
            "figures", 
            "fig-geo-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion 
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp)

@@

ggsave(here("analysis",
            "figures", 
            "fig-geo-us-focus-by-year.png"),
       bg ="white",
       h = 5, # experiment with h and w to get the right size and proportion 
       w = 6,
       units = "in",
       dpi = 900) # make the image nice and crisp)

@@

ggsave(here("analysis",
            "figures", 
            "fig-topic-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))

@@

ggsave(here("analysis",
            "figures", 
            "fig-method-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))
```

@@

# how many schools did we match with the CC data
uni_name %>% 
  filter(!is.na(basic2021)) %>% 
  nrow() # 245, 290, 300, 313, 404 / 433 for US unis

@@

ggplot(uni_name_tally) +
  aes(reorder(Category, n), n) +
  geom_col() +
  coord_flip() +
  xlab("") +
  theme_minimal(base_size = 14)

>>>>

ggsave(here("analysis",
            "figures", 
            "fig-panel-per-year.png"),
       bg ="white",
       h = 15, # experiment with h and w to get the right size and proportion 
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp

@@

ggsave(here("analysis",
            "figures", 
            "fig-geo-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion 
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp)

@@

ggsave(here("analysis",
            "figures", 
            "fig-geo-us-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion 
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp)

@@

ggsave(here("analysis",
            "figures", 
            "fig-topic-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp))

@@

ggsave(here("analysis",
            "figures", 
            "fig-method-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp))
```

@@

# how many schools did we match with the CC data
uni_name %>% 
  filter(!is.na(basic2021)) %>% 
  nrow() # 245, 290, 300, 313, 404, 430 / 433 for US unis

@@

uni_name_tally %>% 
  mutate(Category = str_wrap(Category, width = 30)) %>% 
ggplot() +
  aes(reorder(Category, n), n) +
  geom_col() +
  coord_flip() +
  xlab("") +
  theme_minimal(base_size = 14)

ggsave(here("analysis",
            "figures", 
            "fig-carnegie-classification.png"),
       bg ="white",
       h = 7, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))
